Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-04-22 ms.tex
I added postage stamps of zoom-ins where we have apertures and stars.
I added postage stamps to show the centroiding with centroid_2g.

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/postage_stamps.pdf}
\caption{Postage stamps of apertures used for each source (before centroiding).}\label{fig:starPostageGuess}
\end{centering}
\end{figure}

Source centroiding was performed with \texttt{centroid\_2g} within \texttt{photutils} to do 2-D Gaussian fitting. Figure \ref{fig:starPostageCen}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/postage_stamps_centered.pdf}
\caption{Postage stamps of apertures used for each source, after centroiding with \texttt{centroid\_2g} with the initial guesses shown in Figure \ref{fig:starPostageGuess}.}\label{fig:starPostageCen}
\end{centering}
\end{figure}
